Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-02-24 xrb2/paper.tex
addressed the last comment on the stable burning with high crustal temperatures

In contrast to the models with $T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$, $\tt{F500\_4E8}$ 
is so hot that the organized flame structure is lost. The fuel layer undergoes stable burning and 
essentially simmers in place, rather than forming a flame. This process has been observed in 
neutron stars with accretion rates that exceed the Eddington limit 
\citep{fujimoto1981,bildsten1998thermonuclear,keek2009effect}; in this model we have essentially 
recreated the conditions found in such stars with high accretion rates. This model burns so 
strongly that it is only run out to $40~\mathrm{ms}$. After an initial period when the burning 
moves across the domain, residual burning continues and eventually ignites the entire fuel layer at 
late times, as shown in Figures \ref{fig:4e8_stacked_enuc} and \ref{fig:4e8_stacked_abar} for three 
snapshots taken in the last ten seconds of the simulation. In Figure~\ref{fig:4e8_stacked_enuc}, 
$\enucdot$ reaches values of $10^{18} - 10^{20}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ 
across the domain and at heights up to $\sim 0.5\times 10^4~\mathrm{cm}$. There is still 
significant burning occurring even higher, with $\enucdot$ reaching $\sim 
10^{15}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ at heights up to $\sim 0.8\times 
10^4~\mathrm{cm}$. For comparison, the next hottest run ($\tt{F500\_3E8}$) only reaches maximum 
$\enucdot$ values on the order of $10^{18}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ 
(see Figure~\ref{fig:maxima}, right panel), even at the latest timesteps ($\sim 
70~\mathrm{ms}$, when the flame is most developed). Significant $\enucdot$ values for 
all runs other than $\tt{F500\_4E8}$ are confined to the flame front, rather than spanning the entire domain.

>>>>

In contrast to the models with $T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$, $\tt{F500\_4E8}$ 
is so hot that the organized flame structure is lost. \deleted{The fuel layer undergoes stable burning and 
essentially simmers in place, rather than forming a flame. This process has been observed in 
neutron stars with accretion rates that exceed the Eddington limit 
\citep{fujimoto1981,bildsten1998thermonuclear,keek2009effect}; in this model we have essentially 
recreated the conditions found in such stars with high accretion rates.} This model burns so 
strongly that it is only run out to $40~\mathrm{ms}$. After an initial period when the burning 
moves across the domain, residual burning continues and eventually ignites the entire fuel layer at 
late times, as shown in Figures \ref{fig:4e8_stacked_enuc} and \ref{fig:4e8_stacked_abar} for three 
snapshots taken in the last ten seconds of the simulation. In Figure~\ref{fig:4e8_stacked_enuc}, 
$\enucdot$ reaches values of $10^{18} - 10^{20}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ 
across the domain and at heights up to $\sim 0.5\times 10^4~\mathrm{cm}$. There is still 
significant burning occurring even higher, with $\enucdot$ reaching $\sim 
10^{15}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ at heights up to $\sim 0.8\times 
10^4~\mathrm{cm}$. For comparison, the next hottest run ($\tt{F500\_3E8}$) only reaches maximum 
$\enucdot$ values on the order of $10^{18}~\mathrm{erg}\,\mathrm{g}^{-1} \mathrm{s}^{-1}$ 
(see Figure~\ref{fig:maxima}, right panel), even at the latest timesteps ($\sim 
70~\mathrm{ms}$, when the flame is most developed). Significant $\enucdot$ values for 
all runs other than $\tt{F500\_4E8}$ are confined to the flame front, rather than spanning the entire domain.

\added{Rather than the fuel igniting in a 
localized hot spot and forming a flame which propagates across the domain, for this system the heat produced 
by the high temperature crust alone is sufficient to ignite material across the entire domain. Uniform burning 
across a large fraction of or even the entire surface of the neutron star has been observed in neutron stars 
with accretion rates that exceed the Eddington limit 
\citep{fujimoto1981,bildsten1998thermonuclear,keek2009effect}. However, it is important to note here that the
conditions in our model vary from the conditions that would occur in a neutron star ocean undergoing stable burning 
in a number of ways. Firstly, the model begins without any burning taking place, and initial model assumes that a 
significant amount of unburnt fuel has been able to build up. For a stably burning system, freshly accreted material 
would be continuously burnt, so there would be much less unburnt fuel available. Secondly, we are only modelling 
a few tens of milliseconds, rather than an ongoing process. We therefore do not demonstrate that this system would 
continue to burn stably if the high crustal temperature were maintained and sufficient fuel continued to be 
available, e.g.~through the continued accretion of fresh material. However, this run does suggest that 
a crust with a sufficiently high temperature can provide enough energy to heat the fuel above it to the point of 
ignition, and it may be that if these conditions were maintained that it would be able to sustain stable burning.}
